# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

```{r echo=TRUE, echo=TRUE}
    ac <- read.csv(unz('activity.zip', filename='activity.csv'),
             colClasses = c("numeric", "Date", "numeric"));
    str(ac);

```



## What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

1. Make a histogram of the total number of steps taken each day

2. Calculate and report the mean and median total number of steps taken per day

```{r}
    require('lattice')

    x <- aggregate(steps ~ date, data=ac, FUN=sum)
    histogram(~steps, data=x, nint=24, main="Activity",
              sub="Total steps each day")

    # calculate mean, median for steps
    steps.mean <- mean(x$steps)
    steps.median <- median(x$steps)

    # and report them
    sprintf("Steps mean: %g", steps.mean)
    sprintf("Steps median: %g", steps.median)

```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
